### 2019-09-28 budget.tex
changes order of information
Doubled Busing

     & Shuttles From Hotel       & I                         & $\$$ 1,000.00             & 2                         & 2                        & 2                         & -                         & $\$$6,000.00             \\

@@

     &                           &                           &                           &                           &\multicolumn{3}{r}{Grand Total:}                                                  & $\$$230,984.79           \\

@@

@@

\vspace{2cm}

@@

\subsection{Financial Contingency}
The budget is structured with priority levels outlining the order of cuts, should they be necessary. Priority I expenses are not subject to cuts under any circumstances as they are considered necessities for hosting the conference. Cuts will be made first to reduce most priority IV expenses by half, preserving events while still saving money. Priority III cuts mean eliminating all priority IV expenses and either elimination of, or reduction of the duration of social events by half. Priority II cuts entail complete elimination of social event expenses, along with elimination of tour expenses and reduction of dinner costs through cheaper buffet options and desserts. The expenditure savings from these cuts are outlined in Table *******. While this contingency plan does not consider cuts to the reimbursement funds, this could be reconsidered if necessary, since reimbursements were set aside at a level nearly double that of previous conferences. \\

\begin{tabular}{lrrr}
  \hline\hline
  \multicolumn{1}{l}{Level of Cuts Made} & \multicolumn{1}{c}{Amount Saved} & \multicolumn{1}{c}{Grand Total} & \multicolumn{1}{c}{\% of Max Revenue} \\ \hline\hline 
  Priority IV Cuts Made & $\$$9,346.00 & $\$$221,638.79 & ********** \\
  III and IV Cuts Made & $\$$22,987.25 &$\$$207,997.54 & ********* \\
  II, III, and IV Cuts Made & $\$$49,053.19 & $\$$181,931.60 & ********* \\

>>>>

     & Shuttles From Hotel       & I                         & $\$$ 1,000.00             & 4                         & 4                        & 4                         & -                         & $\$$12,000.00            \\

@@

     &                           &                           &                           &                           &\multicolumn{3}{r}{Grand Total:}                                                  & $\$$236,984.79           \\

@@

\subsection{Financial Contingency}

\begin{tabular}{lrrr}
  \hline\hline
  \multicolumn{1}{l}{Level of Cuts Made} & \multicolumn{1}{c}{Amount Saved} & \multicolumn{1}{c}{Grand Total} & \multicolumn{1}{c}{\% of Max Revenue} \\ \hline\hline 
  Priority IV Cuts Made & $\$$9,346.00 & $\$$227,638.79 & ********** \\
  III and IV Cuts Made & $\$$22,987.25 &$\$$213,997.54 & ********* \\
  II, III, and IV Cuts Made & $\$$49,053.19 & $\$$187,931.60 & ********* \\
\end{tabular}

The budget is structured with priority levels outlining the order of cuts, should they be necessary. Priority I expenses are not subject to cuts under any circumstances as they are considered necessities for hosting the conference. Cuts will be made first to reduce most priority IV expenses by half, preserving events while still saving money. Priority III cuts mean eliminating all priority IV expenses and either elimination of, or reduction of the duration of social events by half. Priority II cuts entail complete elimination of social event expenses, along with elimination of tour expenses and reduction of dinner costs through cheaper buffet options and desserts. The expenditure savings from these cuts are outlined in Table *******. While this contingency plan does not consider cuts to the reimbursement funds, this could be reconsidered if necessary, since reimbursements were set aside at a level nearly double that of previous conferences. \\

@@

\vspace{1cm}

@@
